Associations between chlorophyll *a* and various microcystin health advisory

### 2016-05-26 manuscript/manuscript.Rmd
more edits and data

knit_hooks$set(tab.cap = function(before, options, envir) {
                  if(!before) { 
                    paste('\n\n:', options$tab.cap, sep='') 
                  }
                })https://github.com/USEPA/Microcystinchla/blob/master/R/get_nla.R
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == FALSE) {
    x
  } else
    default_output_hook(x,options)
})
```

@@

#mc_chla[4] <- get_chla(who_rec_low1_cp,0.5)
epa_child <- NULL
who_drink <- NULL
epa_adult <- NULL
who_rec <- NULL
cps<- seq(0.1,0.9,0.1)
for(i in 1:9){
  epa_child[i] <- get_chla(epa_child_cp,cps[i])[1]
  who_drink[i] <- get_chla(who_drink_cp,cps[i])[1]
  epa_adult[i] <- get_chla(epa_adult_cp,cps[i])[1]
  who_rec[i] <- get_chla(who_rec_low1_cp,cps[i])[1]
}
mc_chla<-cbind(epa_child,who_drink,epa_adult,who_rec)
mc_chla_rnd <- mc_chla[mc_chla>0.1]
#Agreement Tables
child_conmat<-conmat_to_df(table(chla=nla_dat$CHLA>=mc_chla[5,1],
                                 mcsyt=nla_dat$MCYST_TL_UGL>=0.3))
child_conmat$tots<-child_conmat[,1]+child_conmat[,2]
child_conmat[3,]<-child_conmat[1,]+child_conmat[2,]

@@

```{r microcystin_levels,echo=FALSE,results='asis', tab.cap="Various suggested microcystin health advisory concentrations. \\label{tab:microcystin_levels}"}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_conc_table)#,format="latex")
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \\textit{a} concentrations that are associated with a 50% probability of exceeding a microcystin health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child", "WHO Drink", 
                      "USEPA Adult", "WHO Recreational")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_chla_tbl)#,format="latex")
```

>>>>

knit_hooks$set(tab.cap = function(before, options, envir) {
                  if(!before) { 
                    paste('\n\n:', options$tab.cap, sep='') 
                  }
                })
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == FALSE) {
    x
  } else
    default_output_hook(x,options)
})
```

@@

#mc_chla[4] <- get_chla(who_rec_low1_cp,0.5)
epa_child <- NULL
who_drink <- NULL
epa_adult <- NULL
who_rec <- NULL
cps<- seq(0.1,0.9,0.1)
for(i in 1:9){
  epa_child[i] <- get_chla(epa_child_cp,cps[i])[1]
  if(epa_child[i]>0.1){epa_child[i]<-round(epa_child[i])}
  who_drink[i] <- get_chla(who_drink_cp,cps[i])[1]
  if(who_drink[i]>0.1){who_drink[i]<-round(who_drink[i])}
  epa_adult[i] <- get_chla(epa_adult_cp,cps[i])[1]
  if(epa_adult[i]>0.1){epa_adult[i]<-round(epa_adult[i])}
  who_rec[i] <- get_chla(who_rec_low1_cp,cps[i])[1]
  if(who_rec[i]>0.1){who_rec[i]<-round(who_rec[i])}
}

mc_chla<-cbind(as.character(epa_child),as.character(who_drink),
               as.character(epa_adult),as.character(who_rec))

#Agreement Tables
child_conmat<-conmat_to_df(table(chla=nla_dat$CHLA>=mc_chla[5,1],
                                 mcsyt=nla_dat$MCYST_TL_UGL>=0.3))
child_conmat$tots<-child_conmat[,1]+child_conmat[,2]
child_conmat[3,]<-child_conmat[1,]+child_conmat[2,]

@@

```{r microcystin_levels,echo=FALSE,results='asis', tab.cap="Various suggested microcystin health advisory concentrations. \\label{tab:microcystin_levels}"}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
order <- c(4,5,6,7,2,1,3)
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration,order) %>%
  arrange(order) %>%
  select(source_of_stnd,type_of_stnd,concentration)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_conc_table)#,format="latex")
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \\textit{a} concentrations that are associated with a 50% probability of exceeding a microcystin health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child (0.3 $\\mu$g/L)", "WHO Drink (1 $\\mu$g/L)", "USEPA Adult (1.6 $\\mu$g/L)", "WHO Recreational (2 $\\mu$g/L) ")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_chla_tbl)#,format="latex")
```
